### 2014-04-05 R/Neutral_simul.Rmd
Clean source add fragments

# Multifractal patterns for spatial neutral simulacions based on BCI

@@

"Because common local species are likely to be
widespread metacommunity species, a better estimate can
often be obtained from fitting only the common species in
the local community." Hubell pag 300

```{r addCoccoliShermanBCI}
# BCI folder data
#
BCIwd <- "~/Dropbox/BCI"

getwd(oldcd)
# "~/Dropbox/Multifractals/NaturalCommunities"

@@

# Parametro theta de Etienne 2007 
N=500*500
a=260
lsf <- rand.neutral(N,a)
ff <- data.frame(sp="",FreqT=as.numeric(lsf),prob=0,Ord=1:length(lsf),Type="Etienne")
tot1 <-rbind(tot1,ff)

require(ggplot2)
g <- ggplot(data=tot1,aes(x=Ord,y=log(FreqT),col=Type)) + geom_line()

g
#lsf <- function(x) log(rad.logserf(tot1[tot1$Type=="BCI",]$Freq,a)(x))
#g + stat_function(fun=lsf)
#g

# Select only the raw data
#
tot1 <-tot1[tot1$Type=="BCI",]

rm(lsf,ff,tot)
```

>>>>

# Multifractal analysis of multispecies spatial distributions - Model simulations

I generate parameter files for the simulation of neutral/hierarchical model using logseries as the metacommunity distribution

```{r generateLogSerParms}

oldcd <-getwd()
source("R/Neutral_fun.r")

# Generate a SAD for metacommunity using a logseries 
#
# side is the side of the simulation lattice
#
# N is the total number of individuals 
#
# S is the species richness 
#

require(untb)
side <- 500
N <- side*side
S <- 450 
ff<-fisher.ecosystem(N=N,S=S,nmax=N)
plot(ff)
nrow(ff)
ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff))
ff$prob <- ff$FreqT/sum(ff$FreqT)

# Parameters
#
# Mortality = 0.2 - 0.4
# Mean Dispersal distance 25  -> Exponential kernel parm  0.04
#                         2.5 -> 0.4
# Colonization = 0.001 -0.0001
# Replacement  = 0 - 1

setwd("Simul")
#undebug(genNeutralParms)
# First generate de inp file with species and metacommunity parameters 
genNeutralParms("fishE",500,ff$prob,1,0.2,0.04,0.001)

# Then pomac.lin to simulate a range of parmeters and repetitions.
#
# Generates pomac.lin for exponential dispersal to compare hierarchical and neutral communities 
# and see when they have similar H and compare if they have similar SAD

genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,1))

# we need the par file with the simulations parameters

par <- read.table("sim.par",quote="",stringsAsFactors=F)
# Change base name
par[par$V1=="baseName",]$V2 <- "Exp452"
# Change model type
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated

# I have to run the model with the parameter ReplacementRate turned on!! take care

@@

```{r addCoccoliShermanBCI}

rm(list = ls())

# BCI folder data
#
BCIwd <- "~/Dropbox/Projects/BCI"

oldcd <-getwd()
# "~/Dropbox/Multifractals/NaturalCommunities"

@@

# Parametro theta de Etienne 2007 
N=500*500*4 # assume a metacommunity with 1.000.000
a=260
lsf <- rand.neutral(N,a)
ff <- data.frame(sp="",FreqT=as.numeric(lsf),prob=0,Ord=1:length(lsf),Type="Etienne")
tot1 <- tot1[tot1$Type!="Etienne",]
tot1 <-rbind(tot1,ff)

require(ggplot2)
ggplot(data=tot1,aes(x=Ord,y=log(FreqT),col=Type)) + geom_line()

#lsf <- function(x) log(rad.logserf(tot1[tot1$Type=="BCI",]$Freq,a)(x))
#g + stat_function(fun=lsf)
#g

# Select only the raw data BCI+Cocoli+Sherman
#
tot1 <-tot1[tot1$Type=="BCI",]

rm(lsf,ff,tot,bci4)
```
